Gyrochronal and Lithium Ages for Stars and Planets Observed by Kepler

### 2023-06-05 paper/ms.tex
minor

{\it Subgiants}---We flagged stars as possible subgiants if they had
$\log g < 4.2$.  We determined this threshold by examining the
relevant flag from \citet{berger_2018_radii_evolnstates},
cross-matched against \citet{Berger_2020a_catalog}.
\citet{berger_2018_radii_evolnstates} performed this classification
using the PARSEC evolutionary models, stellar radii, and DR25 stellar
properties catalog effective temperatures \citep{Mathur_2017}.

@@

{\it Crowding}---We searched the Gaia DR3 point source catalog for
stars within 1 Kepler pixel (4$''$) of every target star.
While many such companions are not physically associated with the
target star, their presence can bias stellar parameters and stellar
rotation period measurements.
We therefore flag any stars with neighbors down to 10$|times$ the 
brightness of the target star within this region ($\Delta G < 2.5$).

>>>>

{\it Subgiants}---We flagged stars as possible subgiants if they had
$\log g < 4.2$.  We set this threshold by examining the
relevant flag from \citet{berger_2018_radii_evolnstates},
cross-matched against \citet{Berger_2020a_catalog}.
\citet{berger_2018_radii_evolnstates} performed this classification
using the PARSEC evolutionary models, stellar radii, and DR25 stellar
properties catalog effective temperatures \citep{Mathur_2017}.

@@

{\it Crowding}---We searched the Gaia DR3 point source catalog for
stars within 1 Kepler pixel (4$''$) of every target star.
While many such companions are not physically associated with the
target star, their presence can bias stellar parameters and stellar
rotation period measurements.
We therefore flag any stars with neighbors down to 10$\times$ the 
brightness of the target star within this region ($\Delta G < 2.5$).
